The \emph{FrobeniusThresholds} package for \emph{Macaulay2}

### 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
Minor changes to package and paper

% \begin{center}
% {\large \textbf{The \emph{FrobeniusThresholds} package for \emph{Macaulay2}}}
% \end{center}

@@

@@

\subsection*{Acknowledgements.}  First and foremost, the authors enthusiastically thank all authors and contributors to the \emph{FrobeniusThresholds} package.
Our package coauthors are Dan Smolkin {\color{red}(LIST MORE NAMES)}, and Zhibek Kadyrsizova, Moty Katzman {\color{red} (LIST MORE NAMES)} contributed valuable code to the package.
%Erin Bela, Juliette Bruce, Sara Malec, Maral Mostafazadehfard, Marcus Robinson, Matthew Mastroeni

The \emph{FrobeniusThresholds} package builds heavily upon the \emph{TestIdeals} package for \emph{Macaulay2} \cite{TestIdealsPackage, TestIdealsPaper,M2}, which provides a broad range of functionality for effective computation in prime characteristic commutative algebra.  In fact, both this package and \emph{TestIdeals} are derived from an older package \emph{PosChar}.

@@

\begin{enumerate}
\item Add more cases to {\tt UseSpecialAlgorithms}.
\item Write a function that will extract from this sequences $\{ \nu_f^{\idealm}(p^e) \}_{e=1}^{\infty}$ roots of Bernstein-Sato polynomials.  Especially, strata.

>>>>

@@

Finally, we point out that the  \emph{FrobeniusThresholds} package builds heavily upon the \emph{TestIdeals} package for \emph{Macaulay2} \cite{TestIdealsPackage, TestIdealsPaper,M2}, which provides a broad range of functionality for effective computation in prime characteristic commutative algebra.  In fact, both this package and \emph{TestIdeals} are derived from an older package \emph{PosChar}.

@@

\subsection*{Acknowledgements.}  First and foremost, the authors enthusiastically thank all authors and contributors to the
\emph{FrobeniusThresholds} package.  {\color{red} (CHECK THESE NAMES)}
Our package coauthors are Juliette Bruce and Daniel Smolkin.  Erin Bela, Zhibek Kadyrsizova, Moty Katzman, Sara Malec, and Marcus Robinson also contributed valuable code to the package.

@@

\begin{enumerate}
\item Add more cases to {\tt UseSpecialAlgorithms}.
\item Add the capability to compute non-local {\tt fpt} and non-local {\tt nu} via an option.
\item Write a function that will extract from this sequences $\{ \nu_f^{\idealm}(p^e) \}_{e=1}^{\infty}$ roots of Bernstein-Sato polynomials.  Especially, strata.
